---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bioread

This library provides an R interface to reading AcqKnowledge files collected using a BIOPAC data recording system. It uses reticulate to get data from the underlying python package:

[https://github.com/uwmadison-chm/bioread](https://github.com/uwmadison-chm/bioread)

## Installation

You can install the development version of bioread from GitHub:

```{r install}

# install.packages("devtools")
devtools::install_github("uwmadison-chm/rbioread")
library(bioread)

# Check the installation
reticulate::py_module_available("bioread")

```

## Example

To load an .acq file and plot the first channel with nice names and labels:

```{r example, echo = FALSE}

acq_file <- system.file("extdata", "physio-5.0.1-c.acq", package = "bioread")
acq_data <- bioread::read_acq(acq_file)

channel <- acq_data$channels[[1]]

# Plot the first channel
plot(
   channel$time, channel$data, type = "l", xlab = "Time (s)",
   ylab = channel$units, main = channel$name)
```

## Advanced usage

Using reticulate to access the raw bioread functions and data structures is not much more difficult.

```{r reticulate}

acq_file <- system.file("extdata", "physio-5.0.1-c.acq", package = "bioread")

py_bioread <- reticulate::import("bioread")
py_acq_reader <- py_bioread$reader$Reader$read_headers(acq_file)

py_acq_reader$channel_dtype_headers[[1]]$numpy_dtype(TRUE)
```

Remember that if you are passing list or array indexes as parameters to python
functions, you will need to use 0-based indexing:

```{r indexing}

acq_file <- system.file("extdata", "physio-5.0.1-c.acq", package = "bioread")

py_bioread <- reticulate::import("bioread")
py_acq_data <- py_bioread$read(acq_file, channel_indexes = 1:2)

for (i in 1:length(py_acq_data$channels)) {
  cat("Channel", i, "loaded:", py_acq_data$channels[[i]]$loaded, "\n")
}

# Oops, we accidentally loaded channels 2 and 3
```
## Getting help

For most "this .acq file won't load" issues, you'll want to go to [the original Python repository](https://github.com/uwmadison-chm/bioread) and open an issue.

If the problem seems to be more on the R end of things, drop a note in this one.

