---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bioread

This library provides an R interface to reading AcqKnowledge files collected using a BIOPAC data recording system. It uses reticulate to get data from the underlying python package:

[https://github.com/uwmadison-chm/bioread](https://github.com/uwmadison-chm/bioread)

## Installation

You can install the development version of bioread from GitHub:

``` r

# install.packages("devtools")
devtools::install_github("uwmadison-chm/rbioread")

```

## Example

To load an .acq file and plot the first channel with nice names and labels:

```{r example, echo = FALSE}
acq_file = system.file("extdata", "physio-5.0.1-c.acq", package = "bioread")
acq_data <- bioread::read_acq(acq_file)

channel <- acq_data$channels[[1]]

# Plot the first channel
plot(
   channel$time, channel$data, type = "l", xlab="Time (s)",
   ylab = channel$units, main = channel$name)
```

## Advanced usage

Using reticulate to access the raw bioread functions and data structures is not too much more difficult:

```{r reticulate}

acq_file = system.file("extdata", "physio-5.0.1-c.acq", package = "bioread")

py_bioread = reticulate::import("bioread")
py_acq_reader = py_bioread$reader$Reader$read_headers(acq_file)

py_acq_reader$version_string
```

## Getting help

For most "this .acq file won't load" issues, you'll want to go to [the original Python repository](https://github.com/uwmadison-chm/bioread) and open an issue.

If the problem seems to be more on the R end of things, drop a note in this one.

